Combinatorial interpretations of holonomic recurrences

### 2021-08-29 article/main.tex
Add minor fixes

\subsection{Generating functions}%
\label{sub:generating_functions}

@@

Note that in order to compute \(k\)-th element of the sequence, \(a_k\), we just need to find a constant corresponding to indeterminate \(z^k\).

\begin{example}
    \label{ex:bin_gf}
    Having our recursive definition of the object, we can easily construct a generating function for it. Let's create a generating function that will count the number of full binary trees consisting of exactly \(k\) internal nodes.

@@

Note that we used \(z\) to count internal nodes and left the leaf part as \(1\).

@@

\subsection{Holonomic recurrences}%
\label{sub:holonomic_recurrences}

@@

\begin{example}
    \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because:
    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0\]
\end{example}

@@

\begin{definition}[\cite{complexity}]
    \label{def:holo_2}
    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists generating function in the following form:
    \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
    for some fixed \(r \in \N\); \(b, p_0, \ldots, p_r \in \poly\) not all identical to zero.
\end{definition}

Equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}.\cite{complexity}

>>>>

\subsection{Generating functions}%
\label{sub:generating_functions}
\todo{Make the section simpler}

@@

Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find a constant corresponding to indeterminate \(z^k\).

\begin{example}
    \label{ex:bin_gf}
    Having our recursive definition of the object, we can easily construct a generating function for it. Let's create a generating function that will count the number of full binary trees consisting of exactly \(k\) internal nodes.\todo{define sequence for the structure}

@@

Note that we used \(z\) to mark internal nodes. Leaves are of size \(0\), so they are marked using \(z^0 = 1\).

@@

\subsection{Holonomic recurrences}%
\label{sub:holonomic_recurrences}
\todo{Extend the section}

@@

\begin{example}
    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisifies:
    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0\]
\end{example}

@@

\begin{definition}[\cite{complexity}]
    \label{def:holo_2}
    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a generating function in the following form:
    \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
    for some fixed \(r \in \N\); \(b, p_0, \ldots, p_r \in \poly\) not all identical to zero.
\end{definition}

The equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}.\cite{complexity}
